The mass relations between supermassive black holes and their host galaxies at $1< z<2$ with \hst-WFC3

### 2019-11-21 manuscript/manuscript.tex
Remove the bold face

\begin{eqnarray}
\label{eq:Hb}
\log \left(\frac{\mathcal M_{\rm BH}(H\beta) }{M_{\odot}}\right)&~=~& 6.91+0.50\log \left(\frac{ \rm L _{\lambda_{5100}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
&~+~& 2.0 \log \left(\frac{\rm FWHM({\bf H\beta })}{1000 ~{\rm km~s^{-1}}}\right) .
\end {eqnarray}

@@

We compare the morphology of AGNs host galaxies to inactive galaxies from the {\bf CANDELS survey~\citep{Grogin2011, Koekemoer2011}.} We identify 4401 inactive galaxies within a redshift range ($1.2<z<1.7$), comparable to our AGN sample, whose \sersic\ measurements are provided by \citet{VDwel++2012} using \galfit. Their stellar masses are derived based on the {\bf 3-D-\hst\ spectroscopic survey~\citep{Momcheva2016, Brammer2012} } and comparable to our AGN hosts ($9.5< \log (M_* /M_{\odot})< 11.5$; Section~\ref{sec:mm}). We compare the histogram of the inferred \Reff\ and \sersic\ index to the inactive galaxies in Figure~\ref{fig:hist_rn}, where we find no significant difference between their distributions and median value. We also test whether the distributions can be drawn from the same parent population using a Kolmogorov-Smirnov test and determining the p-value to be 0.42 and 0.04 for \Reff\ and $n$, respectively. We conclude that the host galaxies of our AGN sample are representative of the overall population of galaxies, with a significant disk component, at comparable luminosity and stellar mass at the same redshift. In Section~\ref{sec:bh_bulge}, we use this information to infer the likely bulge masses, hence the \mbh\ -- \bmass\ relation.

@@

\bibliographystyle{apj.bst}
%\bibliography{references}
\input{manuscript.bbl}

@@

\begin{deluxetable*}
{@{\extracolsep{0pt}}lcccccccc}   % need for the gap between the clines.
\tablecolumns{9}
\tablewidth{0pt}
\tablecaption{AGN properties} 
\tablehead
{ 
\colhead{Target ID}&
  \multicolumn{4}{c}{\halpha ~emission line}&
  \multicolumn{4}{c}{\hbeta ~emission line} \\
  \cline{2-5}  \cline{6-9} \\
\colhead{}& 
\colhead{{\bf FWHM($H\alpha$)}}& \colhead{$\log( \rm L _{H\alpha}$)}& \colhead{$\log$\mbh}& Eddington ratio &
\colhead{{\bf FWHM($H\beta$)}}& \colhead{$\log( \rm L _{\lambda5100})$}& \colhead{$\log$\mbh}& Eddington ratio \\
\colhead{}& 
\colhead{(\kms)}& \colhead{(${\rm erg~s^{-1}}$)}& 
\colhead{(M$_{\odot}$)}& (log$( L_{\rm Bol}/L_{\rm Edd})$)&
\colhead{(\kms)}& 
\colhead{(${\rm erg~s^{-1}}$)}&\colhead{(M$_{\odot}$)} & (log$(L_{\rm Bol}/L_{\rm Edd})$)\\
\colhead{(1)}& 
\colhead{(2)}& \colhead{(3)}& 
\colhead{(4)}& \colhead{(5)}& 
\colhead{(6)}&\colhead{(7)}&
\colhead{(8)}& \colhead{(9)}
}
\startdata 
CID1174 & 1906 & 43.43 & 7.99 & -0.47 & 5898 & 44.76 & 8.83& -1.34 \\
CID1281 & 1619 & 43.24 & 7.75 & -0.41 & \nodata & \nodata & \nodata & \nodata \\
CID206 & 3334 & 43.48 & 8.53 & -0.97 & \nodata & \nodata & \nodata& \nodata \\
CID216 & 2230 & 42.85 & 7.85 & -0.90 & \nodata & \nodata & \nodata& \nodata \\
CID237 & 2112 & 43.86 & 8.29 & -0.36 & \nodata & \nodata & \nodata& \nodata \\
CID255 & 1932 & 43.99 & 8.27 & -0.22 & 3709 & 45.37 & 8.73& -0.60 \\
CID3242 & 2543 & 43.83 & 8.45 & -0.55 & 3775 & 45.10 & 8.61& -0.75 \\
CID3570 & 1959 & 43.16 & 7.89 & -0.63 & \nodata & \nodata & \nodata& \nodata \\
CID452 & 3458 & 42.92 & 8.30 & -1.26 & 3127 & 44.63 & 8.22& -0.88 \\
CID454 & 2824 & 43.34 & 8.31 & -0.88 & \nodata & \nodata & \nodata& \nodata \\
CID50 & 2340 & 43.94 & 8.42 & -0.42 & 1939 & 45.33 & 8.15& -0.06 \\
CID543 & 2189 & 43.57 & 8.19 & -0.53 & \nodata & \nodata & \nodata& \nodata \\
CID597 & 1656 & 43.33 & 7.81 & -0.39 & \nodata & \nodata & \nodata& \nodata \\
CID607 & 3009 & 43.67 & 8.53 & -0.78 & 4242 & 44.78 & 8.56& -1.04 \\
CID70 & 2480 & 43.51 & 8.27 & -0.68 & 3982 & 45.16 & 8.69& -0.77 \\
LID1273 & 3224 & 43.61 & 8.56 & -0.87 & \nodata & \nodata & \nodata& \nodata \\
LID1538 & 2941 & 43.60 & 8.47 & -0.79 & \nodata & \nodata & \nodata& \nodata \\
LID360 & 2482 & 43.88 & 8.45 & -0.50 & 2869 & 45.09 & 8.37& -0.52 \\
XID2138 & 3186 & 43.61 & 8.55 & -0.86 & 2945 & 44.81 & 8.25& -0.71 \\
XID2202 & 2973 & 43.56 & 8.46 & -0.82 & \nodata & \nodata & \nodata& \nodata \\
XID2396 & 2271 & 44.06 & 8.46 & -0.33 & 2658 & 45.50 & 8.51& -0.24 \\
CDFS-1 & 2000 & 43.02 & 7.83 & -0.03 & \nodata & \nodata & \nodata& \nodata \\
CDFS-229 & 2190 & 43.60 & 8.20 & -0.60 & \nodata & \nodata & \nodata& \nodata \\
CDFS-321 & 2442 & 43.93 & 8.46 & -0.46 & \nodata & \nodata & \nodata& \nodata \\
CDFS-724 & 2541 & 42.95 & 8.03 & -1.15 & \nodata & \nodata & \nodata& \nodata \\
ECDFS-358 & 2237 & 43.40 & 8.12 & -0.64 & \nodata & \nodata & \nodata& \nodata \\
SXDS-X1136 & 2760 & 43.43 & 8.33 & -0.81 & 6761 & 44.71 & 8.93& -1.49 \\
SXDS-X50 & 1817 & 43.42 & 7.94 & -0.43 & \nodata & \nodata & \nodata& \nodata \\
SXDS-X717 & 2931 & 43.05 & 8.20 & -1.05 & \nodata & \nodata & \nodata& \nodata \\
SXDS-X735 & 2702 & 43.70 & 8.44 & -0.67 & 3520 & 45.07 & 8.54& -0.70 \\
SXDS-X763 & 2961 & 43.57 & 8.47 & -0.81 & 4509 & 44.51 & 8.47& -1.29 \\
SXDS-X969 & 2296 & 43.50 & 8.20 & -0.61 & 1696 & 45.05 & 7.90& -0.08 \\
\enddata
\label{tab:result_mbh}
\tablecomments{
Column 1: Object ID.
Column 2-5: \halpha\ emission line width (FWHM), \halpha\ luminosity, inferred \mbh\ and Eddington ratio. %(or continuum line at $\rm L _{\lambda5100}$)
Column 6-9: \hbeta\ emission line BH properties. 
The typical uncertainty level for FWHM is $15\%$, and for $\log( \rm L _{\lambda})$ is in the range $0.01\sim0.2$~dex, respectively. The inferred uncertainty level for \mbh\ are assumed as 0.4 dex.
}
\end{deluxetable*}

>>>>

\begin{eqnarray}
\label{eq:Hb}
\log \left(\frac{\mathcal M_{\rm BH}(H\beta) }{M_{\odot}}\right)&~=~& 6.91+0.50\log \left(\frac{ \rm L _{\lambda_{5100}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
&~+~& 2.0 \log \left(\frac{\rm FWHM(H\beta)}{1000 ~{\rm km~s^{-1}}}\right) .
\end {eqnarray}

@@

We compare the morphology of AGNs host galaxies to inactive galaxies from the CANDELS survey~\citep{Grogin2011, Koekemoer2011}. We identify 4401 inactive galaxies within a redshift range ($1.2<z<1.7$), comparable to our AGN sample, whose \sersic\ measurements are provided by \citet{VDwel++2012} using \galfit. Their stellar masses are derived based on the 3-D-\hst\ spectroscopic survey~\citep{Momcheva2016, Brammer2012} and comparable to our AGN hosts ($9.5< \log (M_* /M_{\odot})< 11.5$; Section~\ref{sec:mm}). We compare the histogram of the inferred \Reff\ and \sersic\ index to the inactive galaxies in Figure~\ref{fig:hist_rn}, where we find no significant difference between their distributions and median value. We also test whether the distributions can be drawn from the same parent population using a Kolmogorov-Smirnov test and determining the p-value to be 0.42 and 0.04 for \Reff\ and $n$, respectively. We conclude that the host galaxies of our AGN sample are representative of the overall population of galaxies, with a significant disk component, at comparable luminosity and stellar mass at the same redshift. In Section~\ref{sec:bh_bulge}, we use this information to infer the likely bulge masses, hence the \mbh\ -- \bmass\ relation.

@@

\bibliographystyle{apj.bst}
\bibliography{references}
%\input{manuscript.bbl}

@@

\begin{deluxetable*}
{@{\extracolsep{0pt}}lcccccccc}   % need for the gap between the clines.
\tablecolumns{9}
\tablewidth{0pt}
\tablecaption{AGN properties} 
\tablehead
{ 
\colhead{Target ID}&
  \multicolumn{4}{c}{\halpha ~emission line}&
  \multicolumn{4}{c}{\hbeta ~emission line} \\
  \cline{2-5}  \cline{6-9} \\
\colhead{}& 
\colhead{FWHM($H\alpha$)}& \colhead{$\log( \rm L _{H\alpha}$)}& \colhead{$\log$\mbh}& Eddington ratio &
\colhead{FWHM($H\beta$)}& \colhead{$\log( \rm L _{\lambda5100})$}& \colhead{$\log$\mbh}& Eddington ratio \\
\colhead{}& 
\colhead{(\kms)}& \colhead{(${\rm erg~s^{-1}}$)}& 
\colhead{(M$_{\odot}$)}& (log$( L_{\rm Bol}/L_{\rm Edd})$)&
\colhead{(\kms)}& 
\colhead{(${\rm erg~s^{-1}}$)}&\colhead{(M$_{\odot}$)} & (log$(L_{\rm Bol}/L_{\rm Edd})$)\\
\colhead{(1)}& 
\colhead{(2)}& \colhead{(3)}& 
\colhead{(4)}& \colhead{(5)}& 
\colhead{(6)}&\colhead{(7)}&
\colhead{(8)}& \colhead{(9)}
}
\startdata 
CID1174 & 1906 & 43.43 & 7.99 & -0.47 & 5898 & 44.76 & 8.83& -1.34 \\
CID1281 & 1619 & 43.24 & 7.75 & -0.41 & \nodata & \nodata & \nodata & \nodata \\
CID206 & 3334 & 43.48 & 8.53 & -0.97 & \nodata & \nodata & \nodata& \nodata \\
CID216 & 2230 & 42.85 & 7.85 & -0.90 & \nodata & \nodata & \nodata& \nodata \\
CID237 & 2112 & 43.86 & 8.29 & -0.36 & \nodata & \nodata & \nodata& \nodata \\
CID255 & 1932 & 43.99 & 8.27 & -0.22 & 3709 & 45.37 & 8.73& -0.60 \\
CID3242 & 2543 & 43.83 & 8.45 & -0.55 & 3775 & 45.10 & 8.61& -0.75 \\
CID3570 & 1959 & 43.16 & 7.89 & -0.63 & \nodata & \nodata & \nodata& \nodata \\
CID452 & 3458 & 42.92 & 8.30 & -1.26 & 3127 & 44.63 & 8.22& -0.88 \\
CID454 & 2824 & 43.34 & 8.31 & -0.88 & \nodata & \nodata & \nodata& \nodata \\
CID50 & 2340 & 43.94 & 8.42 & -0.42 & 1939 & 45.33 & 8.15& -0.06 \\
CID543 & 2189 & 43.57 & 8.19 & -0.53 & \nodata & \nodata & \nodata& \nodata \\
CID597 & 1656 & 43.33 & 7.81 & -0.39 & \nodata & \nodata & \nodata& \nodata \\
CID607 & 3009 & 43.67 & 8.53 & -0.78 & 4242 & 44.78 & 8.56& -1.04 \\
CID70 & 2480 & 43.51 & 8.27 & -0.68 & 3982 & 45.16 & 8.69& -0.77 \\
LID1273 & 3224 & 43.61 & 8.56 & -0.87 & \nodata & \nodata & \nodata& \nodata \\
LID1538 & 2941 & 43.60 & 8.47 & -0.79 & \nodata & \nodata & \nodata& \nodata \\
LID360 & 2482 & 43.88 & 8.45 & -0.50 & 2869 & 45.09 & 8.37& -0.52 \\
XID2138 & 3186 & 43.61 & 8.55 & -0.86 & 2945 & 44.81 & 8.25& -0.71 \\
XID2202 & 2973 & 43.56 & 8.46 & -0.82 & \nodata & \nodata & \nodata& \nodata \\
XID2396 & 2271 & 44.06 & 8.46 & -0.33 & 2658 & 45.50 & 8.51& -0.24 \\
CDFS-1 & 2000 & 43.02 & 7.83 & -0.03 & \nodata & \nodata & \nodata& \nodata \\
CDFS-229 & 2190 & 43.60 & 8.20 & -0.60 & \nodata & \nodata & \nodata& \nodata \\
CDFS-321 & 2442 & 43.93 & 8.46 & -0.46 & \nodata & \nodata & \nodata& \nodata \\
CDFS-724 & 2541 & 42.95 & 8.03 & -1.15 & \nodata & \nodata & \nodata& \nodata \\
ECDFS-358 & 2237 & 43.40 & 8.12 & -0.64 & \nodata & \nodata & \nodata& \nodata \\
SXDS-X1136 & 2760 & 43.43 & 8.33 & -0.81 & 6761 & 44.71 & 8.93& -1.49 \\
SXDS-X50 & 1817 & 43.42 & 7.94 & -0.43 & \nodata & \nodata & \nodata& \nodata \\
SXDS-X717 & 2931 & 43.05 & 8.20 & -1.05 & \nodata & \nodata & \nodata& \nodata \\
SXDS-X735 & 2702 & 43.70 & 8.44 & -0.67 & 3520 & 45.07 & 8.54& -0.70 \\
SXDS-X763 & 2961 & 43.57 & 8.47 & -0.81 & 4509 & 44.51 & 8.47& -1.29 \\
SXDS-X969 & 2296 & 43.50 & 8.20 & -0.61 & 1696 & 45.05 & 7.90& -0.08 \\
\enddata
\label{tab:result_mbh}
\tablecomments{
Column 1: Object ID.
Column 2-5: \halpha\ emission line width (FWHM), \halpha\ luminosity, inferred \mbh\ and Eddington ratio. %(or continuum line at $\rm L _{\lambda5100}$)
Column 6-9: \hbeta\ emission line BH properties. 
The typical uncertainty level for FWHM is $15\%$, and for $\log( \rm L _{\lambda})$ is in the range $0.01\sim0.2$~dex, respectively. The inferred uncertainty level for \mbh\ are assumed as 0.4 dex.
}
\end{deluxetable*}
